Untitled

### 2020-11-20 ms/manuscript.Rmd
Add t-test for responses between generations

```{r load-data}
loadd(
  list = c(
    "climate",
    "filmy_species",
    "moorea_sites",
    "phylosig",
    "range_types"
  )
)
```

@@

@@

Ability to recover from desiccation was tested in sporophytes of 15 species and gametophytes of 14 species, including 12 species with both life phases (Appendix S3).
A general correlation of DT with habitat was observed in sporophytes (Fig. 4).
Both terrestrial species (*Abrodictyum dentatum* (Bosch) Ebihara & K Iwats.
and *C. apiifolia*) lacked even moderate DT, and failed to recover from the gentlest treatment of 2 d at --38 MPa (more stringent tests were not conducted on these species after confirming their lack of DT at this level).
Saxicolous species (*Crepidomanes kurzii* (Bedd.) Tagawa & K.
Iwats., *Polyphlebium endlicherianum* (C. Presl) Ebihara & K.
Iwats., and *Vandenboschia maxima* (Blume) Copel.) also had low DT; only *C. kurzii* was able to recover from desiccation up to --86 MPa for 2 d but not more.
All epiphytic species were capable of recovering from desiccation to a certain degree, but ability varied between species.
Most low elevation epiphytes could not tolerate long periods (15 d) of desiccation; only *Crepidomanes bipunctatum* (Poir.) Copel.
was able to recover from desiccation longer than 2 d.
Most of the high elevation epiphytes could recover from 2 d treatments regardless of desiccation intensity (except for *H.* *pallidum* and *P.* *borbonicum*, which failed to recover from 2 d at --282 MPa), and many could withstand desiccation for 15 d.
Interestingly, *C. minutum* var.
2, *Hymenophyllum multifidum* (G. Forst.) Sw., and *Hymenophyllum polyanthos* (Sw.) Sw.
could recover from desiccation at --86 or --282 MPa for 15 d, but not --38 MPa.

>>>>

```{r load-data}
loadd(
  list = c(
    "climate",
    "filmy_species",
    "moorea_sites",
    "phylosig",
    "range_types",
    "recovery_species_means"
  )
)
```

@@

```{r dt-stats}
# Count number of species included in DT test by generation
n_dt_species_gameto <- recovery_species_means %>% 
  count(species, generation) %>% 
  count(generation) %>% 
  filter(generation == "gameto") %>% 
  pull(n) %>% english2

n_dt_species_gameto <- recovery_species_means %>% 
  count(species, generation) %>% 
  count(generation) %>% 
  filter(generation == "sporo") %>% 
  pull(n) %>% english2

n_dt_species_both <- recovery_species_means %>% 
  count(species, generation) %>% 
  group_by(species) %>% 
  summarize(n_generation = n_distinct(generation), .groups = "drop") %>%
  filter(n_generation == 2) %>%
  pull(species) %>%
  n_distinct() %>%
  english2

# Vector of species that I know *after* running the t-test have significant
# differences and discuss in the MS.
species_with_signif_dt_diff <- c("Hymenophyllum_polyanthos", "Hymenophyllum_digitatum", "Crepidomanes_minutum2", "Polyphlebium_endlicherianum", "Polyphlebium_borbonicum")

t_test_results %>% 
  filter(response == "recover", p_value < 0.05) %>%
  # Make sure that species with signif diff in DT mentioned
  # in MS match those in the actual analysis results
  verify(setequal(.$species, species_with_signif_dt_diff)) %>%
  select(species, estimate, p_value) %>%
  arrange(p_value)

Ability to recover from desiccation was tested in sporophytes of `r n_dt_species_gameto` species and gametophytes of `r n_dt_species_gameto` species, including `r n_dt_species_both` species with both life phases (Appendix S3).
A general correlation of DT with habitat was observed in sporophytes (Fig. 4).
Both terrestrial species (*Abrodictyum dentatum* (Bosch) Ebihara & K Iwats. and *C. apiifolia*) lacked even moderate DT, and failed to recover from the gentlest treatment of 2 d at --38 MPa (more stringent tests were not conducted on these species after confirming their lack of DT at this level).
Saxicolous species (*Crepidomanes kurzii* (Bedd.) Tagawa & K. Iwats., *Polyphlebium endlicherianum* (C. Presl) Ebihara & K. Iwats., and *Vandenboschia maxima* (Blume) Copel.) also had low DT; only *C. kurzii* was able to recover from desiccation up to --86 MPa for 2 d but not more.
All epiphytic species were capable of recovering from desiccation to a certain degree, but ability varied between species.
Most low elevation epiphytes could not tolerate long periods (15 d) of desiccation; only *Crepidomanes bipunctatum* (Poir.) Copel. was able to recover from desiccation longer than 2 d.
Most of the high elevation epiphytes could recover from 2 d treatments regardless of desiccation intensity (except for *H.* *pallidum* and *P.* *borbonicum*, which failed to recover from 2 d at --282 MPa), and many could withstand desiccation for 15 d.
Interestingly, *C. minutum* var. 2, *Hymenophyllum multifidum* (G. Forst.) Sw., and *Hymenophyllum polyanthos* (Sw.) Sw. could recover from desiccation at --86 or --282 MPa for 15 d, but not --38 MPa.

@@
